Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip \LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par

### 2022-01-23 paper.tex
(paper) add note on nix for dependency management

% Created 2022-01-23 Sun 15:10
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\section{Introduction}
\label{sec:org94b9d88}

Healthcare data—such as information from clinical trials, disease registries, electronic health records (EHRs), and medical devices—is growing at a compound annual growth rate of 36 percent (\citeprocitem{10}{NCHIT, 2021}). Increasingly, this data helps address 4 challenges associated with healthcare:

@@

At the same time, healthcare consumers are making more decisions and have to navigate an increasingly complex system. Traditionally, diagnosing a patient’s condition has been based heavily on the umbrella approach, which is based solely on the patient-reported symptoms, resulting in an umbrella diagnosis and treatment that frequently fails to achieve their intended effects due to individual variability. As a result, many existing therapies fail to achieve their intended effects due to individual variability. Precision medicine aims to allow tailor prevention and treatment with an individual approach. (\citeprocitem{12}{Ravizza et al., 2019}). Due to the complexity of human biology, individualized medicine requires taking into account aspects that go well beyond standard medical care. Medical care only has a relative contribution of 10 to 20 percent to outcomes; health-related behaviors, socioeconomic factors, and environmental aspects account for the other 80 to 90 percent (\citeprocitem{7}{Magnan \& , 2017}). Computationally, the interdependencies and correlations among these diverse contributors create formidable challenges concerning optimizing treatment effectiveness. (\citeprocitem{8}{McDermott et al., 2012})

Significant investments are being made to deliver the right data and powerful insights at the point of care. Industry incumbents and new entrants alike are trying to create digital experiences that reinforce healthy, preventive behaviors. Despite that, accounting for the exponential possibilities from this diversity of new data is stretching the capabilities of classical computing systems. (\citeprocitem{3}{Grumbling \& Horowitz, 2020}).

\section{AI in Precision Medicine}
\label{sec:org742e6c1}

@@

A key aspect of tailoring medical approaches is proactivity. Early treatments and preventive interventions tend to drastically improve outcomes and optimize costs. Classical machine learning has already shown some promise in predicting the risk of future diseases for a range of patient groups based on EHRs (\citeprocitem{4}{Jauk et al., 2020}). Supervised and unsupervised quantum-enhanced machine learning techniques could allow earlier more accurate, and more granular risk predictions. Eventually, medical practitioners might even have the tools to understand how an individual’s risk for any given condition changes over time, enabled by continual virtual diagnostics based on ongoing data streams from individuals. (\citeprocitem{5}{Kumar et al., 2021})

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org71a1586}

Quantum computers process information in a fundamentally different way from traditional computers. Previous computer technology advancements—such as integrated circuits—enabled faster computing, but were still based on classical information processing. These computers manipulate quantum bits (qubits). These are unlike classical bits, which store information as either a 0 or 1, and they can display uniquely quantum properties, such as entanglement. As a result, it becomes possible to construct quantum algorithms that can outperform their classical counterparts which are not able to leverage quantum phenomena. (\citeprocitem{9}{Montanaro, 2016})

\begin{itemize}
\item Chemistry, machine learning/artificial intelligence (AI), optimization, or simulation tasks. Machine learning has shown potential to be enhanced by quantum computing and is symbiotically helping drive quantum advances (\citeprocitem{2}{Carleo \& Troyer, 2017})
\item Complex correlations and interdependencies among many highly interconnected elements, such as molecular structures in which many electrons interact
\item Inherent scaling limits of relevant classical algorithms. For instance, the resource requirements of classical algorithms may increase exponentially with problem size, as is the case when simulating the time evolution of quantum systems (\citeprocitem{13}{Whitfield et al., 2011}).
\end{itemize}

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:org086bb1c}

@@

The most computationally demanding part of gradient-based algorithms, namely, computing the fitness function and its gradient for control input, can be accomplished by the process of evolution and measurement on quantum hardware. By posing queries to and receiving answers from these devices, classical computing devices update the control parameters until an optimal control solution is found (\citeprocitem{6}{Li et al., 2017}). Using this hybrid approach gives rise to interesting areas of research that seek to leverage the principles of quantum mechanics to augment machine learning or vice-versa. Enabling us to enhance classical ML algorithms by outsourcing difficult calculations to a quantum computer.

@@

\subsection{Generative Adversarial Networks}
\label{sec:orgd77e06b}

Generative Adversarial Networks, or GANs for short, are an approach to generative modeling using deep learning methods, such as convolutional neural networks. Generative modeling is an unsupervised learning task in machine learning that involves automatically discovering and learning the regularities or patterns in input data in such a way that the model can be used to generate or output new examples that plausibly could have been drawn from the original dataset (NO\_ITEM\_DATA:pmlr-v119-choi20a)

GANs are a clever way of training a generative model by framing the problem as a supervised learning problem with two sub-models: the generator model that we train to generate new examples, and the discriminator model that tries to classify examples as either real (from the domain) or fake (generated). The two models are trained together in a zero-sum game, adversarial, until the discriminator model is fooled about half the time, meaning the generator model is generating plausible examples. This can be modeled through the equation

@@

\subsubsection{MolGAN}
\label{sec:orga8067d8}

Existing drug discovery pipelines take 5-10 years and cost billions of dollars. Computational approaches aim to sample from regions of the whole molecular and solid-state compounds called chemical space which could be on the order of 1060. Deep generative models can model the underlying probability distribution of both the physical structures and property of drugs and relate them nonlinearly. By exploiting patterns in massive datasets, these models can distill salient features that characterize the molecules. We can utilize Generative Adversarial Networks (GANs) discover drug candidates by generating molecular structures that obey chemical and physical properties and show affinity towards binding with the receptor for a target disease.

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:orgb971969}

@@

\section{Prototype}
\label{sec:orgb96e059}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:org48e8ed4}

@@

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:orgea9f13d}

@@

\subsection{Data}
\label{sec:org73e7280}

@@

The Molecular data used to train our MolGAN and QuGAN models is the QM9 Dataset obtained from Anatole von Lilienfeld. The dataset contains the computed geometric, energetic, electronic, and thermodynamic properties for 134k stable small organic molecules made up of CHONF. These molecules correspond to the subset of all 133,885 species with up to nine heavy atoms (CONF) out of the GDB-17 chemical universe of 166 billion organic molecules. The model is trained on geometries, corresponding harmonic frequencies, dipole moments, polarizabilities, along with energies and enthalpies. The dataset is hosted on \href{https://doi.org/10.6084/m9.figshare.c.978904.v5}{figshare}.

\subsection{Tools and Hardware}
\label{sec:org42c99db}

The open-source Qiskit framework provides convenient access to multiple quantum simulators as well as a real quantum computer backend. The user can choose to utilize either IBM's cloud-based QASM simulator technology, Google's local equivalent Cirq, and Pennylane's quicker but less accurate lightning simulator. All three backends allow for quick training and testing via quantum simulators and real quantum hardware.

@@

While simulated hardware produces \emph{slightly} different results to actual hardware, the margin is within 1\%. The tests below were conducted using actual IBMQ hardware, on the \verb~ibmq_lima~ quantum computer (\citeprocitem{11}{Quantum, 2021})

@@

@@

\section{Results}
\label{sec:org211e0f6}

\subsection{Speed}
\label{sec:org999cba1}

This is the largest benefit of quantum-accelerated machine learning.  We can see that in both algorithms, quantum computing provided an exponential increase in speed over the non-accelerated counterpart. In the case of QGAN, We can see anywhere from a 8-32\% decrease in the time needed to generate molecules, with the same input parameters. In the case of our QuTorch-HG algorithm, it can process a batch of images within 1/10th of a second, allowing for models to be trained at 95\% accuracy in under 5 minutes! A similar model, written with tensorflow and trained on the same cpu, took 32 minutes to achieve 94.3\% accuracy.

@@

\subsection{Accuracy}
\label{sec:org0734acb}

@@

\subsection{Pricing}
\label{sec:org272e882}

@@

\section{Conclusion and Further Research}
\label{sec:org563e7f0}

As you can see Healthcare data, collected from the many different modalities and locations that surround patients—is underused today. Clinical factors only account for a small percentage of health-relevant data. Therefore, obtaining actionable insights from other areas, including genomics, behavior, and social and environmental influences, is critical.

@@

\section{References}
\label{sec:org0333cf7}

@@

\hypertarget{citeproc_bib_item_3}{Grumbling, E., \& Horowitz, M. (2020). \textit{Quantum computing}. \url{https://doi.org/10.17226/25196}}

\hypertarget{citeproc_bib_item_4}{Jauk, S., Kramer, D., Großauer, B., Rienmüller, S., Avian, A., Berghold, A., Leodolter, W., \& Schulz, S. (2020). Risk prediction of delirium in hospitalized patients using machine learning: An implementation and prospective evaluation study. \textit{Journal of the American Medical Informatics Association}, \textit{27}(9), 1383–1392. \url{https://doi.org/10.1093/jamia/ocaa113}}

\hypertarget{citeproc_bib_item_5}{Kumar, Y., Koul, A., Sisodia, P. S., Shafi, J., Verma, K., Gheisari, M., \& Davoodi, M. B. (2021). Heart failure detection using quantum-enhanced machine learning and traditional machine learning techniques for internet of artificially intelligent medical things. \textit{Wireless Communications and Mobile Computing}, \textit{2021}, 1–16. \url{https://doi.org/10.1155/2021/1616725}}

\hypertarget{citeproc_bib_item_6}{Li, J., Yang, X., Peng, X., \& Sun, C.-P. (2017). Hybrid quantum-classical approach to quantum optimal control. \textit{Physical Review Letters}, \textit{118}(15). \url{https://doi.org/10.1103/physrevlett.118.150503}}

\hypertarget{citeproc_bib_item_7}{Magnan, S., \& . (2017). Social determinants of health 101 for health care: Five plus five. \textit{NAM Perspectives}, \textit{7}(10). \url{https://doi.org/10.31478/201710c}}

\hypertarget{citeproc_bib_item_8}{McDermott, J. E., Wang, J., Mitchell, H., Webb-Robertson, B.-J., Hafen, R., Ramey, J., \& Rodland, K. D. (2012). Challenges in biomarker discovery: combining expert insights with statistical analysis of complex omics data. \textit{Expert Opinion on Medical Diagnostics}, \textit{7}(1), 37–51. \url{https://doi.org/10.1517/17530059.2012.718329}}

\hypertarget{citeproc_bib_item_9}{Montanaro, A. (2016). Quantum algorithms: an overview. \textit{Npj Quantum Information}, \textit{2}(1). \url{https://doi.org/10.1038/npjqi.2015.23}}

\hypertarget{citeproc_bib_item_10}{NCHIT. (2021). \textit{Non-federal acute care hospital electronic health record adoption}. \url{https://www.healthit.gov/data/}}

\hypertarget{citeproc_bib_item_11}{Quantum, I. (2021). \textit{Ibm quantum services}. \url{https://quantum-computing.ibm.com/}}

\hypertarget{citeproc_bib_item_12}{Ravizza, S., Huschto, T., Adamov, A., Böhm, L., Büsser, A., Flöther, F. F., Hinzmann, R., König, H., McAhren, S. M., Robertson, D. H., Schleyer, T., Schneidinger, B., \& Petrich, W. (2019). Predicting the early risk of chronic kidney disease in patients with diabetes using real-world data. \textit{Nature Medicine}, \textit{25}(1), 57–59. \url{https://doi.org/10.1038/s41591-018-0239-8}}

\hypertarget{citeproc_bib_item_13}{Whitfield, J. D., Biamonte, J., \& Aspuru-Guzik, A. (2011). Simulation of electronic structure hamiltonians using quantum computers. \textit{Molecular Physics}, \textit{109}(5), 735–750. \url{https://doi.org/10.1080/00268976.2011.552441}}

NO\_ITEM\_DATA:pmlr-v119-choi20a
\end{hangparas}

>>>>

% Created 2022-01-23 Sun 16:34
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\section{Introduction}
\label{sec:orgfcc4ff3}

Healthcare data—such as information from clinical trials, disease registries, electronic health records (EHRs), and medical devices—is growing at a compound annual growth rate of 36 percent (\citeprocitem{13}{NCHIT, 2021}). Increasingly, this data helps address 4 challenges associated with healthcare:

@@

At the same time, healthcare consumers are making more decisions and have to navigate an increasingly complex system. Traditionally, diagnosing a patient’s condition has been based heavily on the umbrella approach, which is based solely on the patient-reported symptoms, resulting in an umbrella diagnosis and treatment that frequently fails to achieve their intended effects due to individual variability. As a result, many existing therapies fail to achieve their intended effects due to individual variability. Precision medicine aims to allow tailor prevention and treatment with an individual approach. (\citeprocitem{16}{Ravizza et al., 2019}). Due to the complexity of human biology, individualized medicine requires taking into account aspects that go well beyond standard medical care. Medical care only has a relative contribution of 10 to 20 percent to outcomes; health-related behaviors, socioeconomic factors, and environmental aspects account for the other 80 to 90 percent (\citeprocitem{10}{Magnan \& , 2017}). Computationally, the interdependencies and correlations among these diverse contributors create formidable challenges concerning optimizing treatment effectiveness. (\citeprocitem{11}{McDermott et al., 2012})

Significant investments are being made to deliver the right data and powerful insights at the point of care. Industry incumbents and new entrants alike are trying to create digital experiences that reinforce healthy, preventive behaviors. Despite that, accounting for the exponential possibilities from this diversity of new data is stretching the capabilities of classical computing systems. (\citeprocitem{5}{Grumbling \& Horowitz, 2020}).

\section{AI in Precision Medicine}
\label{sec:orgfac4fa0}

@@

A key aspect of tailoring medical approaches is proactivity. Early treatments and preventive interventions tend to drastically improve outcomes and optimize costs. Classical machine learning has already shown some promise in predicting the risk of future diseases for a range of patient groups based on EHRs (\citeprocitem{6}{Jauk et al., 2020}). Supervised and unsupervised quantum-enhanced machine learning techniques could allow earlier more accurate, and more granular risk predictions. Eventually, medical practitioners might even have the tools to understand how an individual’s risk for any given condition changes over time, enabled by continual virtual diagnostics based on ongoing data streams from individuals. (\citeprocitem{7}{Kumar et al., 2021})

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org7fc4a22}

Quantum computers process information in a fundamentally different way from traditional computers. Previous computer technology advancements—such as integrated circuits—enabled faster computing, but were still based on classical information processing. These computers manipulate quantum bits (qubits). These are unlike classical bits, which store information as either a 0 or 1, and they can display uniquely quantum properties, such as entanglement. As a result, it becomes possible to construct quantum algorithms that can outperform their classical counterparts which are not able to leverage quantum phenomena. (\citeprocitem{12}{Montanaro, 2016})

\begin{itemize}
\item Chemistry, machine learning/artificial intelligence (AI), optimization, or simulation tasks. Machine learning has shown potential to be enhanced by quantum computing and is symbiotically helping drive quantum advances (\citeprocitem{2}{Carleo \& Troyer, 2017})
\item Complex correlations and interdependencies among many highly interconnected elements, such as molecular structures in which many electrons interact
\item Inherent scaling limits of relevant classical algorithms. For instance, the resource requirements of classical algorithms may increase exponentially with problem size, as is the case when simulating the time evolution of quantum systems (\citeprocitem{18}{Whitfield et al., 2011}).
\end{itemize}

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:org0849fd0}

@@

The most computationally demanding part of gradient-based algorithms, namely, computing the fitness function and its gradient for control input, can be accomplished by the process of evolution and measurement on quantum hardware. By posing queries to and receiving answers from these devices, classical computing devices update the control parameters until an optimal control solution is found (\citeprocitem{9}{Li et al., 2017}). Using this hybrid approach gives rise to interesting areas of research that seek to leverage the principles of quantum mechanics to augment machine learning or vice-versa. Enabling us to enhance classical ML algorithms by outsourcing difficult calculations to a quantum computer.

@@

\subsection{Generative Adversarial Networks}
\label{sec:org081d75d}

Generative Adversarial Networks, or GANs for short, are an approach to generative modeling using deep learning methods, such as convolutional neural networks. Generative modeling is an unsupervised learning task in machine learning that involves automatically discovering and learning the regularities or patterns in input data in such a way that the model can be used to generate or output new examples that plausibly could have been drawn from the original dataset (\citeprocitem{3}{Choi et al., 2020})

GANs are a clever way of training a generative model by framing the problem as a supervised learning problem with two sub-models: the generator model that we train to generate new examples, and the discriminator model that tries to classify examples as either real (from the domain) or fake (generated). The two models are trained together in a zero-sum game, adversarial, until the discriminator model is fooled about half the time, meaning the generator model is generating plausible examples. This can be modeled through the equation (\citeprocitem{17}{Wang et al., 2020})

@@

\subsubsection{MolGAN}
\label{sec:orgeeeb340}

Existing drug discovery pipelines take 5-10 years and cost billions of dollars. Computational approaches aim to sample from regions of the whole molecular and solid-state compounds called chemical space which could be on the order of 1060. Deep generative models can model the underlying probability distribution of both the physical structures and property of drugs and relate them nonlinearly. By exploiting patterns in massive datasets, these models can distill salient features that characterize the molecules. We can utilize Generative Adversarial Networks (GANs) discover drug candidates by generating molecular structures that obey chemical and physical properties and show affinity towards binding with the receptor for a target disease. (\citeprocitem{8}{Li et al., 2021})

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:org6088837}

@@

\section{Prototype}
\label{sec:orga7b8d9a}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:orga441ff8}

@@

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:org9cb6a28}

@@

\subsection{Data}
\label{sec:org92550b2}

@@

The Molecular data used to train our MolGAN and QuGAN models is the QM9 Dataset obtained from Anatole von Lilienfeld. The dataset contains the computed geometric, energetic, electronic, and thermodynamic properties for 134k stable small organic molecules made up of CHONF. These molecules correspond to the subset of all 133,885 species with up to nine heavy atoms (CONF) out of the GDB-17 chemical universe of 166 billion organic molecules. The model is trained on geometries, corresponding harmonic frequencies, dipole moments, polarizabilities, along with energies and enthalpies. (\citeprocitem{15}{Raghunathan Ramakrishnan et al., 2019})

\subsection{Tools and Hardware}
\label{sec:org7a52c85}

The open-source Qiskit framework provides convenient access to multiple quantum simulators as well as a real quantum computer backend. The user can choose to utilize either IBM's cloud-based QASM simulator technology, Google's local equivalent Cirq, and Pennylane's quicker but less accurate lightning simulator. All three backends allow for quick training and testing via quantum simulators and real quantum hardware (\citeprocitem{4}{Cross, 2018}).

@@

While simulated hardware produces \emph{slightly} different results to actual hardware, the margin is within 1\%. The tests below were conducted using actual IBMQ hardware, on the \verb~ibmq_lima~ quantum computer (\citeprocitem{14}{Quantum, 2021})

@@

Nix and NixOS are used for dependency management, allowing us to create reproducible, binary cached, distributed and non-privileged builds for our software. This also allows for quicker deployments on hardware, and provides stability for the end user, as well as allows us to quickly spin up development environments on unix-based hardware.

@@

\section{Results}
\label{sec:org4ad5b45}

\subsection{Speed}
\label{sec:orgff3949e}

This is the largest benefit of quantum-accelerated machine learning.  We can see that in both algorithms, quantum computing provided an exponential increase in speed over the non-accelerated counterpart. In the case of QGAN, We can see anywhere from a 8-32\% decrease in the time needed to generate molecules, with the same input parameters. In the case of our QuTorch-HG algorithm, it can process a batch of images within 1/10th of a second, allowing for models to be trained at 95\% accuracy in under 5 minutes. A similar model, written with tensorflow and trained on the same cpu, took 32 minutes to achieve 94.3\% accuracy.

@@

\subsection{Accuracy}
\label{sec:orgad86146}

@@

\subsection{Pricing}
\label{sec:org15437c0}

@@

\section{Conclusion and Further Research}
\label{sec:org090a6a7}

Healthcare data, collected from the many different modalities and locations that surround patients—is underused today. Clinical factors only account for a small percentage of health-relevant data. Therefore, obtaining actionable insights from other areas, including genomics, behavior, and social and environmental influences, is critical.

@@

\section{References}
\label{sec:org7d75113}

@@

\hypertarget{citeproc_bib_item_3}{Choi, K., Grover, A., Singh, T., Shu, R., \& Ermon, S. (2020). Fair generative modeling via weak supervision. In H. D. III \& A. Singh (Eds.), \textit{Proceedings of the 37th international conference on machine learning} (Vol. 119, pp. 1887–1898). PMLR. \url{https://proceedings.mlr.press/v119/choi20a.html}}

\hypertarget{citeproc_bib_item_4}{Cross, A. (2018). The ibm q experience and qiskit open-source quantum computing software. \textit{Aps March Meeting Abstracts}, \textit{2018}, L58–003.}

\hypertarget{citeproc_bib_item_5}{Grumbling, E., \& Horowitz, M. (2020). \textit{Quantum computing}. \url{https://doi.org/10.17226/25196}}

\hypertarget{citeproc_bib_item_6}{Jauk, S., Kramer, D., Großauer, B., Rienmüller, S., Avian, A., Berghold, A., Leodolter, W., \& Schulz, S. (2020). Risk prediction of delirium in hospitalized patients using machine learning: An implementation and prospective evaluation study. \textit{Journal of the American Medical Informatics Association}, \textit{27}(9), 1383–1392. \url{https://doi.org/10.1093/jamia/ocaa113}}

\hypertarget{citeproc_bib_item_7}{Kumar, Y., Koul, A., Sisodia, P. S., Shafi, J., Verma, K., Gheisari, M., \& Davoodi, M. B. (2021). Heart failure detection using quantum-enhanced machine learning and traditional machine learning techniques for internet of artificially intelligent medical things. \textit{Wireless Communications and Mobile Computing}, \textit{2021}, 1–16. \url{https://doi.org/10.1155/2021/1616725}}

\hypertarget{citeproc_bib_item_8}{Li, J., Topaloglu, R., \& Ghosh, S. (2021). Quantum generative models for small molecule drug discovery. \textit{Arxiv:2101.03438 [Quant-Ph]}. \url{http://arxiv.org/abs/2101.03438}}

\hypertarget{citeproc_bib_item_9}{Li, J., Yang, X., Peng, X., \& Sun, C.-P. (2017). Hybrid quantum-classical approach to quantum optimal control. \textit{Physical Review Letters}, \textit{118}(15). \url{https://doi.org/10.1103/physrevlett.118.150503}}

\hypertarget{citeproc_bib_item_10}{Magnan, S., \& . (2017). Social determinants of health 101 for health care: Five plus five. \textit{NAM Perspectives}, \textit{7}(10). \url{https://doi.org/10.31478/201710c}}

\hypertarget{citeproc_bib_item_11}{McDermott, J. E., Wang, J., Mitchell, H., Webb-Robertson, B.-J., Hafen, R., Ramey, J., \& Rodland, K. D. (2012). Challenges in biomarker discovery: combining expert insights with statistical analysis of complex omics data. \textit{Expert Opinion on Medical Diagnostics}, \textit{7}(1), 37–51. \url{https://doi.org/10.1517/17530059.2012.718329}}

\hypertarget{citeproc_bib_item_12}{Montanaro, A. (2016). Quantum algorithms: an overview. \textit{Npj Quantum Information}, \textit{2}(1). \url{https://doi.org/10.1038/npjqi.2015.23}}

\hypertarget{citeproc_bib_item_13}{NCHIT. (2021). \textit{Non-federal acute care hospital electronic health record adoption}. \url{https://www.healthit.gov/data/}}

\hypertarget{citeproc_bib_item_14}{Quantum, I. (2021). \textit{Ibm quantum services}. \url{https://quantum-computing.ibm.com/}}

\hypertarget{citeproc_bib_item_15}{Raghunathan Ramakrishnan, Dral, P., Rupp, M., \& O. Anatole Von Lilienfeld. (2019). \textit{Quantum chemistry structures and properties of 134 kilo molecules}. Figshare. \url{https://doi.org/10.6084/M9.FIGSHARE.C.978904.V5}}

\hypertarget{citeproc_bib_item_16}{Ravizza, S., Huschto, T., Adamov, A., Böhm, L., Büsser, A., Flöther, F. F., Hinzmann, R., König, H., McAhren, S. M., Robertson, D. H., Schleyer, T., Schneidinger, B., \& Petrich, W. (2019). Predicting the early risk of chronic kidney disease in patients with diabetes using real-world data. \textit{Nature Medicine}, \textit{25}(1), 57–59. \url{https://doi.org/10.1038/s41591-018-0239-8}}

\hypertarget{citeproc_bib_item_17}{Wang, X., Han, Y., Leung, V. C. M., Niyato, D., Yan, X., \& Chen, X. (2020). Convergence of edge computing and deep learning: A comprehensive survey. \textit{IEEE Communications Surveys \& Tutorials}, \textit{22}(2), 869–904. \url{https://doi.org/10.1109/comst.2020.2970550}}

\hypertarget{citeproc_bib_item_18}{Whitfield, J. D., Biamonte, J., \& Aspuru-Guzik, A. (2011). Simulation of electronic structure hamiltonians using quantum computers. \textit{Molecular Physics}, \textit{109}(5), 735–750. \url{https://doi.org/10.1080/00268976.2011.552441}}
\end{hangparas}
